Chapter3_ideas

### 2019-12-09 results/Chapter3_ideas.Rmd
a bit more work

maisel <- ggplot(mapp.cell.wide, aes(x=mean_rbar, y=mean_rand.rbar))+geom_point()+xlim(c(0,.2))+ylim(c(0,.2))

@@

>>>>

maisel <- ggplot(mapp.cell.wide, aes(x=mean_rbar, y=mean_rand.rbar))+geom_point()+xlim(c(0,.3))+ylim(c(0,.3))
maisel

@@

the random r bar is higher than the real r bar positions. meaning on average the male cell rbar values are lower (less to the middle and more to the ends) -- would this be the same as in female cells?
